\documentclass{resume}

\usepackage[a4paper]{geometry}
\geometry{
left=0.4in,
right=0.4in,
top=0.3in,
bottom=0.3in
}

\usepackage{xurl} 
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{HIMANSHU}

\address{+91 74889 78136 $\cdot$ \href{mailto:himanshu.builds@gmail.com}{himanshu.builds@gmail.com} $\cdot$ Bengaluru, India}
\address{\href{https://www.linkedin.com/in/himanshu-056b461a4/}{linkedin} $\cdot$ \href{https://github.com/razorblade42}{github} $\cdot$ \href{https://main--himanshu-pro.netlify.app/}{himanshu-pro.netlify.app}}

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Indian Institute of Technology, Goa} \hfill 2019 – 2023\\
B.Tech, Computer Science \& Engineering \hfill CGPA: \textbf{8.43 / 10}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\textbf{Software Engineer} \hfill June 2025 – Present\\
One Savings Bank India (OSBI) \hfill \textit{Bengaluru}
\begin{itemize}
    \itemsep-0.6em
    \item Architected Java-based microservices using orchestration patterns for mobile app backend, supporting \textbf{10K+ DAU}.
    \item Led FusionAuth API integration for identity management, cutting onboarding time for web users by \textbf{~40\%}.
    \item Built secure RESTful APIs for biometric workflows handling \textbf{30K+ requests/day} with sub-200ms p99 latency.
    \item Extended GraphQL APIs for mobile, reducing response time by \textbf{35\%} through targeted query optimization.
    \item Deployed services on Azure via Terraform (IaC), using APIM and Mambu for core banking integration.
\end{itemize}

\textbf{Software Engineer} \hfill May 2023 – June 2025\\
Cognam Technologies \hfill \textit{Remote}
\begin{itemize}
    \itemsep-0.6em
    \item Integrated virtual card functionality (ISO8583/Lithic) for wallet activation and PIN management for \textbf{50K+ users}.
    \item Designed configurable multi-step auth (OAuth/OIDC/SMS), reducing unauthorized access incidents by \textbf{~60\%}.
    \item Optimized Criteria JPA queries for reporting, cutting CSV export time for \textbf{1M+ rows from ~45s to <8s}.
    \item Built admin portal with HTMX + Spring Boot, improving operations team task throughput by \textbf{~30\%}.
    \item Implemented multilingual notifications and device fingerprinting, increasing push engagement by \textbf{25\%}.
\end{itemize}

\textbf{Software Engineer Intern} \hfill Apr 2022 – Nov 2022\\
Oxytocin Labs \& Cognam Technologies (Trainee) \hfill \textit{Remote}
\begin{itemize}
    \itemsep-0.6em
    \item Built Node.js/TypeScript APIs and React components for a SaaS ad platform (Clients: Spotify, Amazon).
    \item Enhanced Jinjava engine and used ANTLR to build a linter with semantic validators for a web DSL.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\textbf{Giggle — Real-time Squad Discovery Platform} \hfill \href{https://giggle-web-git-main-razorblade42s-projects.vercel.app/}{(Live)}
\begin{itemize}
    \itemsep-0.6em
    \item Engineered a video discovery platform with geo-sharded matchmaking using hybrid MongoDB/Redis.
    \item Implemented Redlock-based atomic pairing and Redis Hashes, reducing DB overhead by \textbf{~50\%}.
    \item Integrated Agora RTC and Socket.io for low-latency multi-participant video and signaling.
\end{itemize}

\textbf{Learnspac — Learning Management System} \hfill \href{https://master.d23e6ad1u7odbc.amplifyapp.com}{(Live)}
\begin{itemize}
    \itemsep-0.6em
    \item Built a full-stack LMS with in-browser code execution and RBAC using MERN stack and modular REST APIs.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
Core & Java, Spring Boot, Microservices, Hibernate \\
Backend & REST APIs, GraphQL, gRPC, Kafka, Redis \\
Databases & PostgreSQL, MySQL, MongoDB \\
Cloud/DevOps & Azure, AWS, Terraform, Docker, Linux \\
AI / LLM & LangChain, RAG, Agentic AI, OpenAI API, Vector DBs, Prompt Engineering \\
Other & Python, JavaScript, React, Node.js \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}

\begin{itemize}
    \itemsep-0.6em
    \item Ranked \textbf{282nd in India} at Google Hashcode — top competitive programming contest by Google.
    \item CodeChef \textbf{4-star (1800+)} rating; solved \textbf{600+ problems} across LeetCode, Codeforces, and CodeChef.
    \item \textbf{AIR 8,000} in IIT JEE Advanced 2019 — admitted to IIT Goa.
\end{itemize}

\end{rSection}

\end{document}
