\documentclass{resume}

\usepackage[a4paper]{geometry}
\geometry{
left=0.4in,
right=0.4in,
top=0.4in,
bottom=0.4in
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{HIMANSHU}

\address{+91 7488978136 \\ Bengaluru, India} 
\address{\href{mailto:himanshu.builds@gmail.com}{himanshu.builds@gmail.com} \\ 
\href{https://www.linkedin.com/in/himanshu-056b461a4/}{linkedin} \\ 
\href{http://github.com/razorblade42}{github} \\ 
\href{https://main--himanshu-pro.netlify.app/}{www.himanshu.studio}}

\begin{document}
% ----------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech CSE }, Indian Institute of Technology Goa.    
  CGPA: 8.43/10 \hfill {2019 - 2023}\\
Relevant Coursework: Data Structures, Algorithms, Computer Networks, Computer Architecture, Digital Systems, Linear Algebra,Discrete Mathematics, Deep learning and AI.

{\bf Class 12 }, CBSE: Holy Mission Secondary School, Patna, Bihar.      Aggregate: 93.4%  \hfill {2016 - 2018}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} @{\vspace{0.2em}} l }
Soft Skills & Integrity, Dependability, Teamwork, Problem Solving, Time Management \\
Languages/Frameworks & Java, Python, C, C++, JavaScript, Spring Boot, MERN Stack, Hibernate, Fast API \\
DB/Messaging Systems & MySQL, PostgreSQL, MongoDB, Kafka\\
Development Tools & Git, Github, Docker, Linux, IntelliJ, Postman \\
Web Technologies & HTML, CSS, HTMX, JavaScript, React\\
Core Expertise & Backend Development, Microservices Architecture, RESTful APIs, JSON-RPC \\
\end{tabular}

\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer} \hfill June 2025 - Present\\
One Savings Bank India (OSBI) \hfill \textit{Bengaluru}
\begin{itemize}
    \itemsep-0.5em
    \item Architected and developed Java-based microservices using orchestration patterns to power the backend of the bank's new mobile application.

    \item Led backend integration for the mobile app by incorporating FusionAuth APIs for identity management, enabling seamless authentication for existing web platform users.

    \item Built secure RESTful APIs supporting authentication workflows, biometric registration, and biometric login to ensure strong user verification mechanisms.

    \item Optimized and extended existing GraphQL APIs to support mobile application use cases and improve query performance.

    \item Developed backend services leveraging Java, Terraform for infrastructure as code, Microsoft Azure cloud services, APIM for API management, and integrated with the Mambu core banking platform.
\end{itemize}

\textbf{Software Engineer} \hfill May 2023 - June 2025\\
Cognam Technologies \hfill \textit{Remote}
\begin{itemize}
    \itemsep-0.5em
    \item Integrated virtual card functionality in user wallet using ISO8583 and Lithic, enabling transactions and features like card activation, deactivation, PIN change, and limit settings.

    \item Built an admin support portal using HTMX for dynamic UI updates and Spring Boot backend to handle seamless client-server interactions.

    \item Optimized SQL queries via Criteria JPA to extract transaction insights and export large datasets as CSV, improving admin-side data access.

    \item Designed a flexible auth system allowing admin-configured multi-step login flows (OAuth/OIDC, email, SMS) and invitation-based user onboarding with enforced auth sequence.

    \item Enhanced the payment app with multilingual notifications and device tracking to boost platform security and user engagement.
\end{itemize}

\textbf{Software Development Trainee} \hfill June 2022 - Nov 2022\\
Cognam Technologies \hfill \textit{Remote}
\begin{itemize}
    \itemsep-0.5em 
    \item Enhanced the Jinjava templating engine for broader functionality, increasing its applicability.
    \item Utilized ANTLR to build a linter for a web template engine.
    \item Worked on type systems, type inference, and scoping algorithms.
    \item Implemented syntax and semantic validators in JavaScript.
\end{itemize}

\textbf{SDE Intern} \hfill April 2022 – May 2022\\
Oxytocin Labs \hfill \textit{Remote}  
\begin{itemize}
    \itemsep-0.5em 
    \item Contributed to a full-stack ad-making SaaS platform used by clients like Spotify and Amazon.
    \item Built RESTful APIs using Node.js and TypeScript for robust backend functionality and integration.
    \item Developed reusable UI components in React.js to deliver responsive and interactive interfaces.
    \item Integrated backend services with AWS for scalable deployment and improved performance.
    \item Collaborated in agile sprints, feature planning, and end-to-end product delivery lifecycle.
\end{itemize}





\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

  \textbf{Giggle – Squad Discovery Platform} \href{https://giggle-web-git-main-razorblade42s-projects.vercel.app/}{(View)}  
  \begin{itemize}
  \itemsep-0.5em 
      \item Engineered a real-time social discovery platform enabling "Squad-to-Squad" video encounters featuring synchronized cinematic reveals and a geo-sharded matchmaking engine.
      \item Integrated Agora RTC for low-latency multi-participant video streaming and Socket.io for a sub-millisecond global signaling mesh to facilitate ephemeral squad messaging and live
  state synchronization.
      \item Optimized system performance and reliability using a hybrid MongoDB/Redis architecture, implementing Redlock-based atomic pairing and migrating high-frequency session data to
  Redis Hashes to reduce database overhead.
      \item Developed a responsive, "Industrial Minimalist" UX using Next.js 15 and Framer Motion, featuring collapsible workspaces, immersive discovery modes, and a "Gatekeeper" manual
  approval security pipeline.

  \end{itemize}
  
\textbf{Learnspac – Learning Platform} \href{https://master.d23e6ad1u7odbc.amplifyapp.com}{(View)}  
\begin{itemize}
\itemsep-0.5em 
    \item Built a full-stack learning management system enabling institutes to create and manage courses, assignments, and student enrollments seamlessly.
    \item Integrated an in-browser code editor with real-time code execution.
    \item Implemented secure authentication and role-based access control for admins, instructors, and students with customized permissions.
    \item Used MERN stack, designed modular and scalable REST APIs as well as React components to ensure maintainability and support for future feature extensions.

\end{itemize}

\textbf{Unsupervised Chunking (Hindi)} \href{https://github.com/razorblade42/unsupervised-chunking}{(View)}  
\begin{itemize}
\itemsep-0.5em 
    \item Developed an unsupervised algorithm to chunk Hindi sentences and identify syntactic units.
    \item Explored n-gram frequency models and K-means clustering for syntactic analysis.
    \item Focused on improving natural language processing for Hindi sentence structures.
\end{itemize}

\end{rSection}






\begin{rSection}{POSITIONS OF RESPONSIBILITY}

\begin{itemize}
    \itemsep-0.5em 
    \item Mentored a first-year student as part of the student mentorship program.
    \item Led the Go-Corona competition team to develop a game based on the “corona” theme.
    \item Team Lead for the “Learnspac - Learning Platform” project.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------

\begin{rSection}{ACHIEVEMENTS}

\begin{itemize}
    \itemsep-0.5em 
    \item Achieved a CodeChef rating of 1800+ (4-star) and ranked 282 in Google Hashcode, India.
    \item Secured All India Rank 8k in IIT JEE Advanced (2019) and All India Rank 14k in JEE Mains (2019).
    \item Solved 600+ problems on competitive coding platforms such as CodeChef, Codeforces, and LeetCode.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXTRA-CURRICULAR ACTIVITIES
%----------------------------------------------------------------------------------------

\end{document}
